---
title: "Week 9 Data Story Submission"
author: "jingying"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions

### What is the topic that you have finalized? (Answer in 1 or 2 sentences)
The topic I have finalised on is on Starbucks in California, US, and its correlation to race and background of inhabitants in specific cities within its branding. 

### What are the data sources that you have curated so far? (Answer 1 or 2 sentences).
The data source I have obtained is for free, and originates from the following link: https://data.world/alice-c/starbucks 

The data set contains information on the number of Starbucks in each city, combined with census data from ca.gov.

```{r,eval=TRUE,echo=TRUE}
# Data set
library(tidyverse)
Starbucks_Cali <- read.csv("Starbucks in California - City Stats.csv")

# First 10 rows of the data set
head(Starbucks_Cali,10)

```
