---
title: "Week 10 Data Story Submission"
author: "jingying"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions

## Week 9

### What is the topic that you have finalized? (Answer in 1 or 2 sentences)
The topic I have finalised on is on Starbucks in California, US, and its correlation to race and background of inhabitants in specific cities within its branding. 

### What are the data sources that you have curated so far? (Answer 1 or 2 sentences).
The data source I have obtained is for free, and originates from the following link: https://data.world/alice-c/starbucks 

The data set contains information on the number of Starbucks in each city, combined with census data from ca.gov.

```{r,eval=TRUE,echo=TRUE}
# Data set
library(tidyverse)
Starbucks_Cali <- read.csv("Starbucks in California - City Stats.csv")

# First 10 rows of the data set
head(Starbucks_Cali,10)

```

## Week 10

### What is the question that you are going to answer? 
Does Starbucks everyday association and correlation to (the white) race and socioeconomic status offer any insightful reflections on consumer culture, social stratification, and branding?

### Why is this an important question? 

With the implications of the common myth touted by Australian millionaire Tim Gurner that "When I was trying to buy my first home I wasn't buying smashed avocados for 19 bucks and four coffees at $4 each", his claims reflect the identification of Starbucks and its drinks to be commonly associated with affluence in its 'pricey' coffee to be significant to one's savings. According to public perception, Starbucks is a brand commonly associated with white Americans and westerners with leanings towards middle to upper class. Furthermore, as implied by Geraldine Rosa Henderson and Kathy Zhang in The Oxford Handbook of Consumption (2019), Starbucks is a white-aligned brand as a cited case of two men of colour being denied service due to implied ethnoracial prejudice, which also provides some reflections of the social racial dynamics, interactions, and inequality at that time in the US. 


### Which rows and columns of the dataset will be used to answer this question? 

I will use the columns:
ID,	County,	Number of Starbucks,	Starbucks per million inhabitants, Median Age,	Median Household Income	2010, Population	Percentage of white population

As the last two rows of the data set are NA values, as of the writing of this rmd doc, I intend to take into account the rows of 1-431 and work from there. 

